\documentclass[a4paper]{article}

% Import some useful packages
\usepackage[margin=0.5in]{geometry} % narrow margins
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.95}

\title{Peer-review of assignment 5 for \textit{INF3331-ThomasFossoy}}
\author{Kjell Olav Dale, Git-repo INF3331-Kjell, {kodale@ulrik.uio.no} \\
 		Alex Luo, Git-repo INF3331-Alex, {alexlu@ulrik.uio.no}}
\date{Deadline: Tuesday, 10. November 2015, 23:59:59.}

\begin{document}
\maketitle

\section{Review}\label{sec:review}
Mac OSX 10.11.1\\Python version 2.7.10


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.1:  Python implementation of the heat equation}
\begin{itemize}
\item You perform a shallow copy of the array. Replace\\\begin{minted}[bgcolor=LightGray,  fontsize=\footnotesize]{python}
u=u_new
\end{minted}
with\\\begin{minted}[bgcolor=LightGray,  fontsize=\footnotesize]{python}
u = [x[:] for x in u_new]
\end{minted}
\item You start your iteration at \textbf{i = 0} and \textbf{j = 0}, you are supposed to start at \textbf{i = 1} and \textbf{j = 1}.
\item These two errors gives you elevated results. Iterating from \textbf{i = 1} and \textbf{j = 1} lowers your results \textbf{10} degrees from \textbf{283} to \textbf{273} and doing the proper copy of u\_new to u lowers it the last degree to the correct \textbf{272}. These changes makes your solution pass the test with an error of \textbf{0.0011666}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.2: NumPy and C implementations} \label{sec:assignment5.2}
\subsubsection*{Numpy} \label{sec:Numpy}
\begin{itemize}
\item The start of your equation\\\begin{minted}[bgcolor=LightGray,  fontsize=\footnotesize]{python}
u[1:-1,1:-1]=u_new[1:-1,1:-1]= u[1:-1,1:-1]
\end{minted} 
is a bit weird and seems unnecessary, but it does not influence the result, which is correct.
\end{itemize}
\subsubsection*{Weave} \label{sec:Weave}
\begin{itemize}\item Weave imported incorrectly, the proper import would be \\\begin{minted}[bgcolor=LightGray,  fontsize=\footnotesize]{python}
from scipy import weave
\end{minted} 
\item You again start your iterations at \textbf{i = 1} and \textbf{j = 1}(see Pure Python review). You also end your iterations at a hardcoded \textbf{50} and \textbf{100}. This means your implementations will not work for any other rectangle size. In addition the values are wrong as they should be \textbf{m-1} and \textbf{n-1}, in the case of a 50x100 rectangle 49 and 99.
\item Making these changes produces the correct result for your weave implementation.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.3: Testing}\label{sec:assignment5.3}
\begin{itemize}
\item The tests work as expected. However you have implemented the tests in every single solver file. It would be easier if you implemented the tests in a single file where you calculate \textbf{analytic\_u} and \textbf{f}, and then used your other implementations to calculate \textbf{u}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.4:  Develop a user interface}\label{sec:assignment5.4}
\begin{itemize}
\item The UI does not save to file as specified in the assignment unless told to do so. 
\item Aside from that the UI works as expected.
\end{itemize} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.5: Latex report}
\begin{itemize}
\item Describes the work done adequately.
\item The report is missing runtime comparisons and explanation of the differences between the solutions.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.7: Github activity plot}
\begin{itemize}
\item Successfully identifies directory as a git directory or not.
\item Regex successfully retrives the different authors and dates from the log data.
\item The plot did not show for me at first. I changed \textbf{plt.legend()} to \textbf{plt.show()} and it appeared. If it showed for you with legend() it might be a difference in our locales
\item Plot is difficult to read, but I guess it shows what it's supposed to.
\end{itemize}
\subsection{General notes}\label{sec:notes}
\begin{itemize}
\item Docstrings are mostly missing, but are present on the solver functions. The ui file is well documented, but the rest are missing a lot of comments that would have been useful in understanding your thinking.
\item You have some redundant imports and also some imports who are done incorrectly.
\item A lot of your code is oddly placed and repeated unnecessarily, for example the test code, analytic\_u, and f calculations in every solution file. This makes the code difficult to read and follow.
\end{itemize}
Recommendations:
\begin{itemize}
\item Read the assignment text more thoroughly. Some of your errors could have been avoided if you had interpreted the assignment correctly.
\item You should also try to structure your code better, avoiding unnecessary functions and repeating code.
\end{itemize}
\bibliographystyle{plain}
\bibliography{literature}

\end{document}

